---
title: "Assignment3"
author: "Arushi Arora"
date: "9/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Reading the CSV from web and filtering 2 columns `Major` and `Major Code`
```{r}
data <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/grad-students.csv")
major_code = data[[1]]
major_name = data[[2]]
```

---

#### Matching `Major` with `DATA` or `STATISTICS`, Obtaining indices
```{r}
## printing Majors matching DATA and STATISTICS
print(grep(pattern = 'DATA|STATISTICS',value = TRUE, major_name, ignore.case = TRUE))
```

#### Extracing indices of the majors matching `DATA` or `STATISTICS`
```{r}
indices = grep(pattern = 'DATA|STATISTICS', major_name, ignore.case = TRUE)
print(indices)
```


#### Matching `Major` with `DATA` or `STATISTICS`
```{r}
matching_major_code = major_code[indices]
print(matching_major_code)
```



### Q2 : Converting stirng/dataframe to vector

```{r}

raw_data_frame <- data.frame("bell pepper","bilberry","blackberry","blood orange","blueberry","cantaloupe","chili pepper","cloudberry","elderberry","lime","lychee","mulberry","olive","salal berry")
print(raw_data_frame)

finalvector <- as.vector(raw_data_frame)
print(finalvector)
typeof (finalvector)


#test_str = "bell pepper  bilberry     blackberry   blood orange\nblueberry    cantaloupe   chili pepper cloudberry  \nelderberry   lime         lychee       mulberry    \nolive        salal berry"
#print(test_str)

#finaltest <- as.vector(test_str)
#print(finaltest)
#typeof (finaltest)

```

---
### Q3 : Describe, in words, what these expressions will match - a

- (.)\1\1
```{r}

# Because the R language doesn't interpret single escape, the regex will not match groups, instead will directly compare \1
# Regex Meaning in R
# 	The (.) allows us to create a group of any character except \n
# 	The \1 matches  exactly with '\1'
regexpr("(.)\1\1", "a\1\1") 

# General Regex Meaning
# 	The (.) allows us to create a group of any character except \n
# 	The \1 matches the same text as matched by the first group i.e (.)
# 	The \1 again matches the same text as matched by the first group i.e (.)
# 
# Overall, the string should be have identical characters in a multiple characters
# Possible Solutions (general, not R):
# 	aaa  
# 	aaabbb   => Match 1 : aaa   => Match 2 : bbb

# Testing genral regex in R
regexpr("(.)\1\1", "aaa")   # match.length = -1

```

### Q3 : Describe, in words, what these expressions will match - b
- "(.)(.)\\2\\1"
```{r}

# Works will in R language with mactching groups

# " => Overall pattern should start with double quotes like ""
#  (.) => Any character except \n -> group1. Also capture 1
#  (.) => Any character except \n -> group2. Also capture 2
#  \\2 => Escaped string, actual \2 -> character that was matched by capture \2
#  \\1 => Escaped string, actual \1 -> character that was matched by capture \1
# " => Overall pattern should end with double quotes like ""

# Examples strings for regex:
# ""abba"", ""1221""

regexpr('"(.)(.)\\2\\1"', '""abba""')   # match.length != -1 i.e match
```

### Q3 : Describe, in words, what these expressions will match - c
- (..)\1
```{r}
# Because the R language doesn't interprets single escape, the regex will not match groups, instead will directly compare \1

# Regex Meaning
# 	The (..) allows us to create a group of any two character except \n
# Regex Meaning in R
# 	The \1 matches  exactly with '\1'
regexpr("(..)\1", "ab\1")   # match.length != -1 i.e match

# Regex Meaning in General
# 	The \1 matches the same text as matched by the first group i.e the same two characters in first group
regexpr("(..)\1", "abab")   # match.length = -1 (doesn't work with R lang)

# But it work with double escaped characters in R
regexpr("(..)\\1", "abab")  # match.length != -1 i.e match
```

### Q3 : Describe, in words, what these expressions will match - d
- "(.).\\1.\\1"
```{r}

# "(.).\\1.\\1"
# " => Overall pattern should start with double quotes like ""
# (.) => Any character except \n -> group1. Also capture 1
# .   => Any character
# \\1 => Escaped string, actual \1 -> character that was matched by capture \1
# .   => Any character
# \\1 => Escaped string, actual \1 -> character that was matched by capture \1
# " => Overall pattern should end with double quotes like ""
regexpr('"(.).\\1.\\1"', '""azaba""')   # match.length != -1i.e match
```

---
### Q4 : Construct regular expressions - a
```{r}

# Start and end with the same character
print("============ 12131 ============")
regexpr("^(.).*\\1$", "12131")

print("============ avcxa ============")
regexpr("^(.).*\\1$", "avcxa")

print("============ $123@$ ============")
regexpr("^(.).*\\1$", "$123@$")

print("============ avcxab - Shouldn't match ============")
regexpr("^(.).*\\1$", "avcxab")

```

---
### Q4 : Construct regular expressions - b
```{r}

# Contain a repeated pair of letters
print("============ church ============")
regexpr(".*(.{2}).*?(\\1)", "church")

print("============ abchurch ============")
regexpr(".*(.{2}).*?(\\1)", "abchurch")

print("============ abcab ============")
regexpr(".*(.{2}).*?(\\1)", "abcab")

print("============ abc - Shouldn't match ============")
regexpr(".*(.{2}).*?(\\1)", "abc")

```

### Q4 : Contain one letter repeated in at least three places - c
```{r}
print("============ eleven ============")
regexpr(".*([a-zA-Z]).*?(\\1).*?(\\1)", "eleven")

print("============ abcadkam ============")
regexpr(".*([a-zA-Z]).*?(\\1).*?(\\1)", "abcadkam")

print("============ 1abc1sai30wa ============")
regexpr(".*([a-zA-Z]).*?(\\1).*?(\\1)", "1abc1sai30wa")

print("============ 12131 - Shouldn't match because only letters allowed ============")
regexpr(".*([a-zA-Z]).*?(\\1).*?(\\1)", "12131")


```
